Design Document for R Package glmm

### 2016-06-06 NewDesignDoc/DesignDocGLMM.tex
Added bin to cum and 3 derivs but not tested
There is some kind of problem, but I'm going to temp move on bc it's not hurting anything (not implemented anywhere anyway) and I need to do more important things.

I will implement this change in steps. Game plan:
\begin{enumerate}
\item Start by writing the binomial cumulant in R. Check to make sure this calculation is identical to that produced by bernoulli for some parameter value $\eta_i$ and for $ntrials=1$. Check for both $\eta$ positive and negative.
\item Check the three calculations for $ntrials=5$ (or some number other than 1) compared to my by-hand calculation. 
\item Code it in C and check that the calculation is identical to that produced in R for $ntrials=1$ and for $ntrials \neq 1$.
\item The second lowest level will then call binomial.glmm rather than bernoulli.glmm as the family. I will work my way up the levels incorporating ntrials. At the top, I will have a variable to set ntrials = 1 (for now). As I do each layer, I will make sure I get all the same answers from my salamanders problem (or some other bernoulli problem).
\item I will go to the top-most layer, right where the model matrices are being made. The new response vector y will be the first column of the user-provided response. The sum of the two entries in the row will create the vector ntrials. I will check that the salamanders problem gives the same results (when specified as cbind(Mate, 1-Mate)).

>>>>

I will implement this change in steps. Game plan:
\begin{enumerate}
\item Without adding binomial yet, add the ntrials argument to all levels of code so that ntrials can be passed to the cumulant functions and their derivatives. At the top, I will have a variable to set ntrials = 1 (for now). As I do each layer, I will make sure I get all the same answers from my salamanders problem (or some other bernoulli problem).
\item Write the binomial cumulant in R. Do some checks with  both $\eta$ positive and negative.
\begin{enumerate}
 \item Check to make sure this calculation is identical to that produced by bernoulli for some parameter value $\eta_i$ and for $ntrials=1$. 
\item Check  the sum of Bernoulli cumulants equals the binomial cumulant (for ntrials $>1$). 
\item Check finite differences. 
\item Check the three calculations for $ntrials=5$ (or some number other than 1) compared to my by-hand calculation. 
\end{enumerate}
\item Code it in C and check that the calculation is identical to that produced in R for $ntrials=1$ and for $ntrials \neq 1$.
\item I will go to the top-most layer, right where the model matrices are being made. The new response vector y will be the first column of the user-provided response. The sum of the two entries in the row will create the vector ntrials. I will check that the salamanders problem gives the same results (when specified as cbind(Mate, 1-Mate)).
